Massively Parallel Monte Carlo Methods for Discrete Linear and Nonlinear Systems

### 2012-10-31 doc/prelim/presentation/prelim_presentation.tex
added nonlinear preliminaries

@@

>>>>

  \begin{itemize}
  \item We seek solutions of the general nonlinear problem
  \end{itemize}

  \[
  \ve{F}(\ve{u}) = \ve{0}
  \]
  \[
  \ve{u} \in \mathbb{R}^n,\ \ve{F}:\mathbb{R}^N \rightarrow
  \mathbb{R}^N
  \]

  \begin{itemize}
  \item We interpret the exact solution $\ve{u}$ to be the roots of
    $\ve{F}(\ve{u})$
  \item Taylor expand the residuals at the $k+1$ iterate about the $k$
    iterate
  \end{itemize}

  \[
  \ve{F}(\ve{u}^{k+1}) = \ve{F}(\ve{u}^{k}) +
  \ve{F}'(\ve{u}^{k})(\ve{u}^{k+1}-\ve{u}^{k}) +
  \frac{\ve{F}''(\ve{u}^{k})}{2}(\ve{u}^{k+1}-\ve{u}^{k})^2 + \cdots
  \]

  \begin{itemize}
  \item Assert $\ve{u}^{k+1}$ is the exact solution
  \end{itemize}

  \[
  -\ve{F}(\ve{u}^{k}) = \ve{F}'(\ve{u}^{k})(\ve{u}^{k+1}-\ve{u}^{k})
  \]

@@

  \begin{itemize}
  \item $\ve{F}'(\ve{u}^{k})$ is the \textit{Jacobian}
    $\ve{J}(\ve{u})$
  \end{itemize}

  \[
  J_{ij} = \frac{\partial F_i(\ve{u})}{\partial u_j}
  \]

  \begin{itemize}
  \item $(\ve{u}^{k+1}-\ve{u}^{k})$ is the solution update from the
    $k$ iterate to the $k+1$ iterate
  \end{itemize}

  \[
  \delta \ve{u}^k = \ve{u}^{k+1}-\ve{u}^{k}
  \]

  \begin{itemize}
  \item Form Newton's method
  \end{itemize}
  \[
  \ve{J}(\ve{u}) \delta \ve{u}^k = -\ve{F}(\ve{u}^{k})
  \]
  \[
  \ve{u}^{k+1} = \ve{u}^k + \delta \ve{u}^k
  \]
